\documentclass{report}

\usepackage{url}
\usepackage{graphicx}
\usepackage{makeidx}
\usepackage[adobe-utopia]{mathdesign}

\title{GraphicUI Test}

	\begin{document}

		
		The GraphicUI tests consist of hand made tests carefully chosen and recorded
		to prove the functionality of \emph{Pawned}. An scenario will be described in 
		detail, and then we will check that the GraphicUI behaves as expected.
				
		\subsection{Opening \textit{Pawned}} 
		
		Three menus are enabled, with the following submenus: 
		\begin{itemize}
			\item File: \textit{New Game}, \textit{Save Game}, \textit{Load Game}, and 
									\textit{Quit}
			\item Game: \textit{End Game} and \textit{Display Options}  
			\item Help: \textit{User Manual} and \textit{About}
		\end{itemize}
		
		The Save Game and End Game options in the menus are disabled.
		Each submenu except \textit{Display Options} will open a new window. 
		\textit{Display Options} contains a submenu with three options that can be 
		checked individualy (Highlight Movable Pieces, Hightlight Possible Moves, 
		Highlight Last Move). These options are disable from user selection before 
		starting a game.
		
		There is a ToolBar with one button for each of the following options:
		New Game, Load Game, Save Game, and End Game. The Save Game and End Game
		buttons are disabled.
		
		The window can be minimized and closed using the small buttons in the
		upper corner of the window. Maximize is disabled. The main panel 
		should be empty.
		
		The following hot keys are enabled:
				\begin{itemize}
					\item New Game - Ctrl + N
					\item Load Game - Ctrl + O
					\item User Manual - Ctrl + U
					\item Quit - Ctrl + Q
				\end{itemize}		
		 
		 
		\subsubsection{New Game}
			The New Game window can be accessed by either the New Game option in 
			the File menu of the button in the toolbar. For each of the players
			the New Game window has:
			\begin{itemize}
					\item Text field to input the player's name (max 8 char)
					\item Radio buttons to select between Human or Computer
					\item Combo box to select the intelligence level of the Computer
								player (Baby, Kid, Adolescence)
					\item Checkbox to select Timed game 
					\item Spinners to input the time (one spinner for minutes and 
								another for seconds)
				\end{itemize}
			If the Computer radio button is selected, the computer level combo box is enabled.
			Otherwise it is disabled. If the Timed checkbox is selected, then the 
			Time spinners are enabled and can receive an input. Otherwise they 
			are disabled. The spinners are set to receive only a number from 0 to 60 for 
			minutes and from 0 to 59 for seconds.
			
			The New Game window also contains a combo box where the user can select the 
			type of game desired (Standard Antichess, EnCastle Antichess, and Connect N).
			When this window is opened, the default game selected is Standard Antichess and
			two pawn images are displayed, one pawn of each color, to identify the players. 
			If EnCastle Antichess is selected everything stays the same. If Connect N is 
			selected, the pawns change to a red chip and a black chip. A spinner appears to
			the right of the game type combo where the user can select the value \textsl{n} 
			for the Connect N game. The spinner will let you to enter values from 2 to 7.
			
			\subsection{Load Game}
			
			This window is very similar to the New Game window. The differences are:
				\begin{itemize}
					\item There is a read-only text field and a Browse button. The Browse
								button opens a file dialog window that is set to filter XML files.
								The text field is updated after the file is selected from the file
								dialog. 
					\item The Timed checkbox is disable, along with the Time spinner fields.
					\item The game type combo box is disabled.
				\end{itemize}
				
			After selecting a file in the File dialog, the Load Window will refresh and
			show some information about the file selected (assuming the file is valid).
			If the saved game was untimed, then the Timed checkboxs will be unchecked and
			the Time fields disabled. If one of the players was set up with limited time, 
			then its Timed checkbox will be checked and the Time fields will display the
			remaining time it has for playing. If both players were timed, then this
			information will be updated for both. At this point \emph{Pawned} will allow 
			the user to change these options. 
			
			The game type combo box will also be updated with the type of game of the 
			saved file. However, this field will always remain disabled. The spinner for
			selecting the \textsl{n} value for Connect N also remains diabled, but it
			refreshes an shows the n value of a saved Connect N game.
			
			Cases to test for each type of game:
			\begin{itemize}
					\item Untimed game
					\item Only one player untimed.
					\item Two timed players.
				\end{itemize}
			
			Other things to test:			
			\begin{itemize}
					\item If a non existing file is chosen in the File dialog, display an 
								error message box.
					\item If 'OK' is clicked without selecting a file display an error message
								box.
					\item If a corrupted file is tried to be loaded, display an error message box.
				\end{itemize}


			\subsection{Starting new games and changing from game type to game type}
			
			\emph{Pawned} allows you to change from two game environments that are further 
			apart from each other than two variations of Chess. The GraphicUI was tested to 
			assure the easiness of this change.		

	\end{document}